Optimal Duplicate Detection in a Sliding Window

### 2020-03-27 qhtv2.tex
Insert graph + some fixes
Fix graphs

\begin{algorithm}[!ht]
	\caption{SHF Setup, Lookup and Insert}\label{alg:SHF}

@@

\begin{algorithm}[!ht]
	\caption{CSHF, Lookup and Insert}\label{alg:CSHF}

@@

\begin{figure}[!ht]
	\centering
	\input{graphs/bench_shorts.tex}
	\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:shorts}
\end{figure}

The value $w_\text{max}$ can be obtained by solving (numerically) for $\FP^{w_\text{max}} = 1/2$ for a given $M$. We numerically solved the equation $\FP^w = 0.5$ for these two filters, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$. Results are given in Figure~\ref{fig:w_opt} and indicate an approximately linear relationship between $M$ and $w_\text{max}$ for large values of $M$: $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).

\begin{figure}[]
	\input{graphs/w_opt_shf.tex}
	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 0.5 ($\pm 0.001$), for several values of $M$.}\label{fig:w_opt}
\end{figure}

@@

%\begin{figure*}[!ht]
%	\begin{tikzpicture}
%	\begin{groupplot}[
%	group style = {
%		group size = 2 by 1,
%		horizontal sep = 35pt,
%	},
%	axis lines = left,
%	ylabel near ticks,
%	width = 0.4\textwidth,
%	height = 0.27\textwidth,
%	]
%	\input{er_n_artificial}
%	\input{er_n_real}
%	%\input{10e6_sum_zipf}
%	\end{groupplot}
%    \path (top)--(bot) coordinate[midway] (group center);
%%	\node[above,rotate=90] at (group center -| current bounding box.west) {Error rate (\%)};
%	\node[right=1em,inner sep=0pt] at(group center -| current bounding box.east) {\pgfplotslegendfromname{legend_n}};
%	\end{tikzpicture}
%
%%	\input{er_n_artificial}
%	\caption{Error rate (times 100) of DDFs of 1Mb, over a real and artificial stream, depending on the size of the stream, without any sliding window. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
%\end{figure*}

\begin{figure}[!ht]
	\begin{tikzpicture}
	\input{er_n_artificial}
	\end{tikzpicture}
	\caption{Error rate (times 100) of DDFs of 1Mb as a function of stream length. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
\end{figure}

@@

\begin{figure}
	\centering
	[TODO]
	\caption{TODO}
	\label{fig:nwddf-in-wddp}
\end{figure}

@@

\begin{figure}[!ht]
	\input{graphs/compare_queues.tex}
	\caption{Error rate (times 100) of queuing filters as a function of window size, $M=10^5$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
\end{figure}
%\begin{table}[]
%	\begin{tabular}{rccccc}
%			   & $w=1000$ & $w=5000$ & $w=10^4$ & $w=10^5$ & $w=10^6$ \\ \hline
%		QHT    & \textbf{9.84} 	  & \textbf{26.25}	 & \textbf{41.09}	 & \textbf{87.89}	  & 70.76      \\
%		Cuckoo & 84.99	  & 99.94	 & 99.95	 & 99.93	  & 99.80      \\
%		SQF    & 16.73 	  & 48.76	 & 69.25	 & 95.77 	  & \textbf{70.14}     \\
%		SBF    & 54.88 	  & 93.93	 & 97.33	 & 97.41	  & 71.17      \\
%	\end{tabular}
%	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{16}$. For each sliding window, the best performance is written in bold.}\label{tab:comparing_queuing}
%\end{table}

@@

\begin{figure}[!ht]
	\input{graphs/bench_l.tex}
	\caption{Evolution of the error rate of a queueing QHT as a function of $L$, for several window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
\end{figure}

@@

\begin{figure}[!ht]
	\input{graphs/improvement.tex}
	\caption{Comparing performances of QHT and SQF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:improvement}
\end{figure}

@@

\begin{figure*}[!ht]
	\centering
	\input{graphs/stream_size_qht.tex}
	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
\end{figure*}

@@

\begin{figure*}[!ht]
\begin{tikzpicture}
	\begin{semilogxaxis}[legend cell align = left, legend pos=outer north east, xlabel=$w$, ylabel=$\FPR^w + \FNR^w (\times 100)$]
	\addplot[color=teal, mark=triangle] table[x=w,y=Error] {Queueing_Cuckoo.dat};
	\addlegendentry{Q\_Cuckoo};
	\addplot[color=teal, mark=triangle, dashed] table[x=w,y=Error] {Cuckoo.dat};
	\addlegendentry{Cuckoo};
	%%
	\addplot[color=olive, mark=square, mark options = {scale=0.7}] table[x=w,y=Error] {Queueing_StableBloom.dat};
	\addlegendentry{$Q\_SBF$};
	\addplot[color=olive, mark=square, mark options = {scale=0.7}, dashed] table[x=w,y=Error] {SBF.dat};
	\addlegendentry{$SBF$};

@@

\end{tikzpicture}
	\caption{Comparing performances of the Cuckoo and SBF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
\end{figure*}
\end{document}

>>>>

\begin{algorithm}[!h]
	\caption{SHF Setup, Lookup and Insert}\label{alg:SHF}

@@

\begin{algorithm}[!h]
	\caption{CSHF, Lookup and Insert}\label{alg:CSHF}

@@

\begin{figure}[!h]
	\centering
	\input{graphs/bench_shorts.tex}
	\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:shorts}
\end{figure}

The value $w_\text{max}$ can be obtained by solving (numerically) for $\FP^{w_\text{max}} = 1/2$ for a given $M$. We numerically solved the equation $\FP^w = 0.5$ for these two filters, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$. Results
% are given in Figure~\ref{fig:w_opt} and 
indicate an approximately linear relationship between $M$ and $w_\text{max}$ for large values of $M$: $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).

%\begin{figure}[]
%	\input{graphs/w_opt_shf.tex}
%	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 0.5 ($\pm 0.001$), for several values of $M$.}\label{fig:w_opt}
%\end{figure}

@@

%\begin{figure*}[!h]
%	\begin{tikzpicture}
%	\begin{groupplot}[
%	group style = {
%		group size = 2 by 1,
%		horizontal sep = 35pt,
%	},
%	axis lines = left,
%	ylabel near ticks,
%	width = 0.4\textwidth,
%	height = 0.27\textwidth,
%	]
%	\input{er_n_artificial}
%	\input{er_n_real}
%	%\input{10e6_sum_zipf}
%	\end{groupplot}
%    \path (top)--(bot) coordinate[midway] (group center);
%%	\node[above,rotate=90] at (group center -| current bounding box.west) {Error rate (\%)};
%	\node[right=1em,inner sep=0pt] at(group center -| current bounding box.east) {\pgfplotslegendfromname{legend_n}};
%	\end{tikzpicture}
%
%%	\input{er_n_artificial}
%	\caption{Error rate (times 100) of DDFs of 1Mb, over a real and artificial stream, depending on the size of the stream, without any sliding window. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
%\end{figure*}

\begin{figure}[!h]
	\begin{tikzpicture}
	\input{er_n_artificial}
	\end{tikzpicture}
	\caption{Error rate (times 100) of DDFs of 1Mb as a function of stream length. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\input{graphs/compare_qht_bdbf_a2.tex}
	\caption{Error rates for QHT, b\_DBF, and A2. While A2 and b\_DBF were designed and ajusted to the wDDP, this is not the case of QHT. Still, QHT outperforms these filters for some values of $w$.}
	\label{fig:nwddf-in-wddp}
\end{figure}

@@

\begin{figure}[!h]
	\input{graphs/compare_queues.tex}
	\caption{Error rate (times 100) of queuing filters as a function of window size, $M=10^5$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
\end{figure}
%\begin{table}[]
%	\begin{tabular}{rccccc}
%			   & $w=1000$ & $w=5000$ & $w=10^4$ & $w=10^5$ & $w=10^6$ \\ \hline
%		QHT    & \textbf{9.84} 	  & \textbf{26.25}	 & \textbf{41.09}	 & \textbf{87.89}	  & 70.76      \\
%		Cuckoo & 84.99	  & 99.94	 & 99.95	 & 99.93	  & 99.80      \\
%		SQF    & 16.73 	  & 48.76	 & 69.25	 & 95.77 	  & \textbf{70.14}     \\
%		SBF    & 54.88 	  & 93.93	 & 97.33	 & 97.41	  & 71.17      \\
%	\end{tabular}
%	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{16}$. For each sliding window, the best performance is written in bold.}\label{tab:comparing_queuing}
%\end{table}

@@

\begin{figure}[!h]
	\input{graphs/bench_l.tex}
	\caption{Evolution of the error rate of a queueing QHT as a function of $L$, for several window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
\end{figure}

@@

\begin{figure}[!h]
	\input{graphs/improvement.tex}
	\caption{Comparing performances of QHT and SQF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:improvement}
\end{figure}

@@

\begin{figure}[]
	\centering
	\input{graphs/stream_size_qht.tex}
	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
\end{figure}

@@

\begin{figure}[]
\begin{tikzpicture}
	\begin{semilogxaxis}[legend cell align = left,%
		 %legend pos=outer north east, 
	legend style={at={(0.02,0.98)},anchor=north west},%
		 xlabel=$w$, ylabel=$\FPR^w + \FNR^w (\times 100)$]
	\addplot[color=teal, mark=triangle] table[x=w,y=Error] {Queueing_Cuckoo.dat};
	\addlegendentry{Q\_Cuckoo};
	\addplot[color=teal, mark=triangle, dashed] table[x=w,y=Error] {Cuckoo.dat};
	\addlegendentry{Cuckoo};
	%%
	\addplot[color=olive, mark=square, mark options = {scale=0.7}] table[x=w,y=Error] {Queueing_StableBloom.dat};
	\addlegendentry{Q\_SBF};
	\addplot[color=olive, mark=square, mark options = {scale=0.7}, dashed] table[x=w,y=Error] {SBF.dat};
	\addlegendentry{SBF};

@@

\end{tikzpicture}
	\caption{Comparing performances of the Cuckoo and SBF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
\end{figure}
\end{document}
